readme

### 2021-10-29 README.Rmd
Added the starting point of the na_dgm function

- [X] Create a function that read Icetag data stored in a CSV file.
- [X] Add the import_raw_icetage_data as an example to the README file.
- [X] Create a function that computes the degree of functional coupling.
- [X] Add the the dfc as an example to the README file.
- [ ] Create a function that computes the diurnality index.
- [ ] Add the the dfc as an example to the README file.

@@

- [X] Create a function that visualize the actogram.
- [ ] Create a function that visualize the actogram + average activity.
- [ ] Create a function that visualize the actogram + average activity + DFC.

@@

- [X] Define data inside the library
- [X] Add and example about the improt_raw_icetag_data to the README.
- [ ] Create a function to test if a dataset is digiRhythm friendly.
- [ ] Create a proper documentation for the data set.
- [ ] configure data sets with lazy loading
- [ ] Create test functions.

@@

```{r visualize, message=FALSE, warning=FALSE, paged.print=FALSE}
data("df516b_2", package = "digiRhythm")
df <- remove_activity_outliers(df516b_2)
df_act_info(df)
activity = names(df)[2]
start <- "2020-30-04"
end <- "2020-06-05"
save <- TRUE
outputdir <- 'testresults'
outplotname <- 'myplot'
width <- 10
device <- 'tiff'
height <-  5
actogram(data, activity, start, end, save = FALSE,
     outputdir = 'testresults', outplotname = 'actoplot', width = 10,
     height =  5, device = 'tiff')
```

>>>>

- [X] Create a function that read Icetag data stored in a CSV file.
- [X] Add the import_raw_icetage_data as an example to the README file.
- [X] Create a function that computes the degree of functional coupling.
- [X] Add the the dfc as an example to the README file.
- [x] Create a function that computes the diurnality index.
- [x] Add the the dfc as an example to the README file.
- [ ] Consider adding other sample data sets (check which ones appear to have
non-noisy data from the previous analysis and visualizations).
- [ ] Enhance the actogram (from the original codes).
- [ ] Add a function that fills NA values in the activity data set.
- [ ] Add a function that creates a histogram for the significant and harmonic
frequencies within the DFC (Patricia's case).

@@

- [X] Create a function that visualize the actogram.
- [ ] Create a function that visualize the actogram + average activity.
- [ ] Create a function that visualize the actogram + average activity + DFC.
- [ ] Create a function that visualizes all daily activities with control over
the number of columns.

@@

- [X] Define data inside the library
- [X] Add and example about the import_raw_icetag_data to the README.
- [x] Create a function to test if a data set is digiRhythm friendly.
- [x] Create a proper documentation for the data set.
- [x] configure data sets with lazy loading
- [ ] Create test functions for all the functionalities.
- [ ] Add a note about the fact that visualizations were created in a way they
are aligned with the standards of common journals and give details about these 
settings + Add a note where the code can be customized to change these settings.
- [ ] Make a series of videos about the digiRhythm library.

@@

```{r visualize, message=FALSE, warning=FALSE, paged.print=FALSE}
data("df691b_1", package = "digiRhythm")
df <- remove_activity_outliers(df691b_1)
df_act_info(df)
activity = names(df)[2]
start <- "2020-08-25"
end <- "2020-10-11"
save <- TRUE
outputdir <- 'testresults'
outplotname <- 'myplot'
width <- 10
device <- 'tiff'
height <-  5
actogram(df, activity, start, end, save = FALSE,
     outputdir = 'testresults', outplotname = 'actoplot', width = 10,
     height =  5, device = 'tiff')
```
